---
title: "ERCre ATAC/CnT: Gene Body + Enhancers"
output: 
  html_document:
    self_contained: true
editor_options: 
  chunk_output_type: console
---

```{r Packages, results = "hide", warning = FALSE, message=FALSE, echo=FALSE}

suppressPackageStartupMessages({
  library(UpSetR)
  })

```

## DEG overlaps {.tabset}

<br/>

### H vs C

```{r echo=FALSE, message=FALSE}

# Load H vs C promoter diff results
ATAC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/H_vs_C/ATAC_sigDEGGbEn_H_vs_C.csv")
H3K4me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/H_vs_C/H3K4me3_sigDEGGbEn_H_vs_C.csv")
H3K4me1 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/H_vs_C/H3K4me1_sigDEGGbEn_H_vs_C.csv")
H3K27ac <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/H_vs_C/H3K27ac_sigDEGGbEn_H_vs_C.csv")
H3K27me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/H_vs_C/H3K27me3_sigDEGGbEn_H_vs_C.csv")

chromDataList <- list(atac=ATAC, h3k4me3=H3K4me3, h3k4me1=H3K4me1, h3k27ac=H3K27ac, h3k27me3=H3K27me3)

upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### Upregulated genes in H
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```
<br/>

#### Upregulated genes in C
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```

### HC vs CC

```{r echo=FALSE, message=FALSE}

# Load HC vs CC promoter diff results
ATAC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/HC_vs_CC/ATAC_sigDEGGbEn_HC_vs_CC.csv")
H3K4me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/HC_vs_CC/H3K4me3_sigDEGGbEn_HC_vs_CC.csv")
H3K4me1 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/HC_vs_CC/H3K4me1_sigDEGGbEn_HC_vs_CC.csv")
H3K27ac <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/HC_vs_CC/H3K27ac_sigDEGGbEn_HC_vs_CC.csv")
H3K27me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/HC_vs_CC/H3K27me3_sigDEGGbEn_HC_vs_CC.csv")

chromDataList <- list(atac=ATAC, h3k4me3=H3K4me3, h3k4me1=H3K4me1, h3k27ac=H3K27ac, h3k27me3=H3K27me3)

upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### Upregulated genes in HC
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```
<br/>

#### Upregulated genes in CC
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```
 
### HH vs CC

```{r echo=FALSE, message=FALSE}

# Load HH vs CC promoter diff results
ATAC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/HH_vs_CC/ATAC_sigDEGGbEn_HH_vs_CC.csv")
H3K4me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/HH_vs_CC/H3K4me3_sigDEGGbEn_HH_vs_CC.csv")
H3K4me1 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/HH_vs_CC/H3K4me1_sigDEGGbEn_HH_vs_CC.csv")
H3K27ac <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/HH_vs_CC/H3K27ac_sigDEGGbEn_HH_vs_CC.csv")
H3K27me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/HH_vs_CC/H3K27me3_sigDEGGbEn_HH_vs_CC.csv")

chromDataList <- list(atac=ATAC, h3k4me3=H3K4me3, h3k4me1=H3K4me1, h3k27ac=H3K27ac, h3k27me3=H3K27me3)

upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### Upregulated genes in HH
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```
<br/>

#### Upregulated genes in CC
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```

### HHC vs CCC

```{r echo=FALSE, message=FALSE}

# Load HHC vs CCC promoter diff results
ATAC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/HHC_vs_CCC/ATAC_sigDEGGbEn_HHC_vs_CCC.csv")
H3K4me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/HHC_vs_CCC/H3K4me3_sigDEGGbEn_HHC_vs_CCC.csv")
H3K4me1 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/HHC_vs_CCC/H3K4me1_sigDEGGbEn_HHC_vs_CCC.csv")
H3K27ac <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/HHC_vs_CCC/H3K27ac_sigDEGGbEn_HHC_vs_CCC.csv")
H3K27me3 <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/HHC_vs_CCC/H3K27me3_sigDEGGbEn_HHC_vs_CCC.csv")

chromDataList <- list(atac=ATAC, h3k4me3=H3K4me3, h3k4me1=H3K4me1, h3k27ac=H3K27ac, h3k27me3=H3K27me3)

upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### Upregulated genes in HHC
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```
<br/>

#### Upregulated genes in CCC
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("h3k27me3", "h3k27ac", "h3k4me1", "h3k4me3", "atac"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per dataset")

```

### ATAC

```{r echo=FALSE, message=FALSE}

# Load H vs C promoter diff results
H_vs_C <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/H_vs_C/ATAC_sigDEGGbEn_H_vs_C.csv")
HC_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/HC_vs_CC/ATAC_sigDEGGbEn_HC_vs_CC.csv")
HH_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/HH_vs_CC/ATAC_sigDEGGbEn_HH_vs_CC.csv")
HHC_vs_CCC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/ATAC/HHC_vs_CCC/ATAC_sigDEGGbEn_HHC_vs_CCC.csv")

chromDataList <- list(H_vs_C=H_vs_C, HC_vs_CC=HC_vs_CC, HH_vs_CC=HH_vs_CC, HHC_vs_CCC=HHC_vs_CCC)

allDEGs <- lapply(chromDataList, function(x) {x$external_gene_name})
upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### All DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(allDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>


#### Upregulated DEGs 
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>

#### Downregulated DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```

### H3K4me3

```{r echo=FALSE, message=FALSE}

# Load H vs C promoter diff results
H_vs_C <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/H_vs_C/H3K4me3_sigDEGGbEn_H_vs_C.csv")
HC_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/HC_vs_CC/H3K4me3_sigDEGGbEn_HC_vs_CC.csv")
HH_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/HH_vs_CC/H3K4me3_sigDEGGbEn_HH_vs_CC.csv")
HHC_vs_CCC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me3/HHC_vs_CCC/H3K4me3_sigDEGGbEn_HHC_vs_CCC.csv")

chromDataList <- list(H_vs_C=H_vs_C, HC_vs_CC=HC_vs_CC, HH_vs_CC=HH_vs_CC, HHC_vs_CCC=HHC_vs_CCC)

allDEGs <- lapply(chromDataList, function(x) {x$external_gene_name})
upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### All DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(allDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>


#### Upregulated DEGs 
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>

#### Downregulated DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```

### H3K4me1

```{r echo=FALSE, message=FALSE}

# Load H vs C promoter diff results
H_vs_C <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/H_vs_C/H3K4me1_sigDEGGbEn_H_vs_C.csv")
HC_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/HC_vs_CC/H3K4me1_sigDEGGbEn_HC_vs_CC.csv")
HH_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/HH_vs_CC/H3K4me1_sigDEGGbEn_HH_vs_CC.csv")
HHC_vs_CCC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K4me1/HHC_vs_CCC/H3K4me1_sigDEGGbEn_HHC_vs_CCC.csv")

chromDataList <- list(H_vs_C=H_vs_C, HC_vs_CC=HC_vs_CC, HH_vs_CC=HH_vs_CC, HHC_vs_CCC=HHC_vs_CCC)

allDEGs <- lapply(chromDataList, function(x) {x$external_gene_name})
upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### All DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(allDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>


#### Upregulated DEGs 
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>

#### Downregulated DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```

### H3K27ac

```{r echo=FALSE, message=FALSE}

# Load H vs C promoter diff results
H_vs_C <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/H_vs_C/H3K27ac_sigDEGGbEn_H_vs_C.csv")
HC_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/HC_vs_CC/H3K27ac_sigDEGGbEn_HC_vs_CC.csv")
HH_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/HH_vs_CC/H3K27ac_sigDEGGbEn_HH_vs_CC.csv")
HHC_vs_CCC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27ac/HHC_vs_CCC/H3K27ac_sigDEGGbEn_HHC_vs_CCC.csv")

chromDataList <- list(H_vs_C=H_vs_C, HC_vs_CC=HC_vs_CC, HH_vs_CC=HH_vs_CC, HHC_vs_CCC=HHC_vs_CCC)

allDEGs <- lapply(chromDataList, function(x) {x$external_gene_name})
upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### All DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(allDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>


#### Upregulated DEGs 
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>

#### Downregulated DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```

### H3K27me3

```{r echo=FALSE, message=FALSE}

# Load H vs C promoter diff results
H_vs_C <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/H_vs_C/H3K27me3_sigDEGGbEn_H_vs_C.csv")
HC_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/HC_vs_CC/H3K27me3_sigDEGGbEn_HC_vs_CC.csv")
HH_vs_CC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/HH_vs_CC/H3K27me3_sigDEGGbEn_HH_vs_CC.csv")
HHC_vs_CCC <- read.csv("~/public/_Projects/AT_HFD_Memory/Epigenetic_memory/ERCre/GB_Enhancers/diffAnalysis/H3K27me3/HHC_vs_CCC/H3K27me3_sigDEGGbEn_HHC_vs_CCC.csv")

chromDataList <- list(H_vs_C=H_vs_C, HC_vs_CC=HC_vs_CC, HH_vs_CC=HH_vs_CC, HHC_vs_CCC=HHC_vs_CCC)

allDEGs <- lapply(chromDataList, function(x) {x$external_gene_name})
upDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "up"), "external_gene_name"]})
downDEGs <- lapply(chromDataList, function(x) {x[which(x$regulation == "down"), "external_gene_name"]})

```

<br/>

#### All DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(allDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>


#### Upregulated DEGs 
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(upDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```
<br/>

#### Downregulated DEGs
<br/>

```{r echo=FALSE, message=FALSE, fig.width=12, fig.height=8}

# Upset plot
upset(fromList(downDEGs), sets = c("HHC_vs_CCC", "HH_vs_CC", "HC_vs_CC", "H_vs_C"),
      order.by = c("freq", "degree"), mb.ratio = c(0.55, 0.45), keep.order = TRUE,
      point.size = 3, line.size = 1, text.scale = c(1,1,1,1,1.5,1.2),
      mainbar.y.label = "DEG intersections", sets.x.label = "DEGs per comparison")

```

### Session information
```{r session_info, echo = FALSE}

devtools::session_info()

```
